# 自然実験

<!-- In this part of the book, we explore a number of issues related to drawing causal inferences from data. -->
本パートでは、データから因果関係を推論する際に関連するいくつかの問題について探求する。
<!-- Many treatments of this topic dive directly into methods, such as instrumental variables or regression discontinuity design.  -->
このトピックに関する多くの論文は、操作変数や回帰不連続デザインなどの方法に直接取り組む。

<!-- Here we have consciously chosen to start with the benchmark setting of randomized experiments and gradually build up to settings where statistical methods may (subject to features of the settings) support credible causal inferences.  -->
ここでは、ランダム化実験のベンチマーク設定から始め、統計的方法が（設定の特徴に応じて）信頼性のある因果関係を支持する可能性がある設定に段階的に移行することを意識的に選択している。
<!-- We believe that carefully thinking about a hypothetical randomized experiment and conjectured causal mechanisms sharpens the thinking needed to successfully bring statistical analyses to bear on problems of causal inference. -->
架空のランダム化実験と推測される因果関係のメカニズムについて慎重に考えることは、統計分析を問題の因果関係に関する問題に適用するために必要な思考を研ぎ澄ますのに役立つと考えている。

<!-- This chapter introduces the concept of the randomized controlled trial and the related idea of the natural experiment.  -->
この章では、ランダム化比較試験の概念とそれに関連する自然実験の概念を紹介する。
<!-- While much discussion focuses on the value of random assignment for causal inference, we explain that other features of an experiment are also of critical importance.  -->
多くの議論が因果関係の推論におけるランダム割り当ての価値に焦点を当てている一方で、実験の他の特徴も重要であることを説明する。
<!-- We explore the question of recognition versus disclosure to illustrate that the framing of the research question itself has important implications for any experiment. -->
認識と開示の問題を探求し、研究問題のフレーミング自体がどんな実験にも重要な影響を与えることを示す。

:::{.callout-tip}
<!-- The code in this chapter uses the packages listed below.  -->
この章のコードでは、以下のパッケージを使用する。
<!-- For instructions on how to set up your computer to use the code found in this book, see Section 1.2.  -->
本書のコードを使用するためにコンピュータを設定する方法については、セクション1.2を参照せよ。
<!-- Quarto templates for the exercises below are available on GitHub. -->
以下の演習問題のQuartoテンプレートはGitHubで入手できる。
:::

```{r}
pacman::p_load(farr, tidyverse)
```



<!-- ## 17.1 Randomized experiments -->
## ランダム化実験

<!-- The randomized experiment is widely regarded to be the “gold standard” of research designs.  -->
ランダム化実験は、研究デザインの中で「最も信頼性の高い方法」として広く認識されている。
<!-- The idea of a randomized experiment is quite simple: observations are randomly assigned to treatment conditions.  -->
ランダム化実験のアイデアは非常にシンプルである：観測値はランダムに処置条件に割り当てられる。
<!-- In the case of a binary treatment variable (i.e., a unit is either treated or not treated), whether a unit is treated is determined by some randomization mechanism, such as a coin toss.  -->
二値の処置変数の場合（つまり、単位が処置されるかどうか）、単位が処置されるかどうかは、コイントスなどのランダム化メカニズムによって決定される。
<!-- In terms of causal diagrams with $X$ being the treatment variable, such randomization implies that there are no arrows into $X$ and thus no confounders that need to be controlled for in estimating causal effects. -->
因果関係ダイアグラムにおいて、$X$が処置変数である場合、このようなランダム化は、$X$に矢印がないことを意味し、因果効果を推定する際に制御する必要がある交絡要因がないことを意味する。

<!-- As a concrete example, let’s consider Jackson et al. (2009).  -->
具体的な例として、Jackson et al. (2009)を考えてみよう。
<!-- From the title (“economic consequences of firms’ depreciation method choice”), we can infer that the treatment of interest is firms’ depreciation method choice.  -->
タイトル（「企業の減価償却方法選択の経済的影響」）から、処置の対象が企業の減価償却方法の選択であることが推測される。
<!-- The specific method choice that Jackson et al. (2009) focus on is accelerated depreciation versus straight-line depreciation, and the outcome (“economic consequence”) of interest is capital investment. -->
Jackson et al. (2009)が焦点を当てる具体的な方法選択は、加速減価償却と直線減価償却であり、興味のある結果（「経済的結果」）は資本投資である。

<!-- In practice, firms are likely to make the choice between accelerated depreciation and straight-line depreciation based on several factors, among which might be the economic depreciation of the relevant assets, the useful life of assets (for assets with shorter lives, the choice is likely to be less important), and various financial reporting incentives (e.g., a growing firm will report higher income in the near term if it uses straight-line depreciation).  -->
実際には、企業は、関連する資産の経済的減価償却、資産の有用寿命（寿命の短い資産の場合、選択は重要ではない可能性がある）、およびさまざまな財務報告のインセンティブ（例：成長する企業は、直線減価償却を使用すると、近い将来に収益が高く報告される）など、いくつかの要因に基づいて、加速減価償却と直線減価償却の選択を行う可能性が高い。
<!-- If any of these conjectured factors affecting depreciation method choice also affects capital investment, then it would confound causal inferences of the kind sought in Jackson et al. (2009). -->
これらの推測される減価償却方法の選択に影響を与える要因が資本投資にも影響を与える場合、Jackson et al. (2009)で求められるような因果推論を混乱させる可能性がある。

<!-- However, if we somehow had the ability to randomly assign firms to either the accelerated depreciation condition or the straight-line depreciation condition, we could draw causal inferences by comparing the capital investment of firms based on the treatment condition to which they were assigned. -->
しかし、何らかの方法で企業を加速減価償却条件または直線減価償却条件にランダムに割り当てる能力があれば、割り当てられた処置条件に基づいて企業の資本投資を比較することで、因果関係を推論することができる。

<!-- There would obviously be challenges in conducting such an experiment.  -->
このような実験を行う際には、明らかにいくつかの課題がある。
<!-- First, we’d likely need to be a regulator with sufficient authority to compel firms to accept the assigned depreciation method.  -->
まず、割り当てられた減価償却方法を受け入れるよう企業に強制するための十分な権限を持つ規制当局である必要があるだろう。
<!-- Even if it had such authority, without a strong desire to understand the effect of depreciation method choice, it’s not clear why a regulator would run such an experiment; and regulators generally have bigger fish to fry.  -->
そのような権限を持っていても、減価償却方法の選択の影響を理解する強い欲求がない場合、なぜ規制当局がそのような実験を行うかは明確ではない。そして、通常、規制当局はより重要な問題に取り組んでいる。
<!-- Some experiments might only require the cooperation of a single firm, but this does not seem to apply for this research question (we would need, say, a firm with many divisions, each with independent investment authority). -->
一部の実験は、単一の企業の協力だけで済むかもしれないが、この研究問題には当てはまらない（例えば、独立した投資権限を持つ多くの部門を持つ企業が必要となる）。

<!-- In practice, the closest we can get to an experiment is a so-called natural experiment, which relies on forces outside the control of the researcher to perform assignment to treatment conditions in a way that is random or, in terms used by Dunning (2012), as-if random. -->
実際には、実験に最も近いのは、研究者のコントロール外の要因に依存して、処置条件への割り当てをランダムまたはDunning (2012)の用語で「あたかもランダム」で行う自然実験と呼ばれるものである。

<!-- In this chapter, we first study the randomized controlled trial, a benchmark form of the randomized experiment.  -->
この章では、まず、ランダム化実験のベンチマーク形式であるランダム化比較試験を研究する。
<!-- We then compare the randomized controlled trial with other forms of experiment, including the natural experiment.  -->
次に、ランダム化比較試験を他の実験形式、自然実験を含む、と比較する。
<!-- To make our discussion of randomized experiments more concrete, we focus on a setting of sustained interest to practitioners and researchers alike: recognition versus disclosure.  -->
ランダム化実験に関する議論を具体的にするために、実務家と研究者の両方にとって興味深い環境である認識と開示に焦点を当てる。
<!-- With this setting in mind, we then turn to a plausible natural experiment used in Michels (2017) and consider what credible inferences this setting supports. -->
この環境を念頭に置いて、Michels (2017)で使用されている可能性のある自然実験に移り、この環境がどのような信頼性のある推論を支持するかを考える。

<!-- ### 17.1.1 Randomized controlled trials as a benchmark -->
### ベンチマークとしてのランダム化比較試行

<!-- A randomized experiment is often implemented in medical sciences as a randomized controlled trial or RCT.  -->
ランダム化実験は、医学においてランダム化比較試行またはRCTとして実施されることが多い。
<!-- Akobeng (2005, p.837) describes an RCT as “a type of study in which participants are randomly assigned to one of two or more clinical interventions.  -->
Akobeng (2005, p.837)は、RCTを「参加者が2つ以上の臨床介入のうちの1つにランダムに割り当てられる研究の一種」と説明している。
<!-- The RCT is the most scientifically rigorous method of hypothesis testing available, and is regarded as the gold standard trial for evaluating the effectiveness of interventions.” -->
RCTは、利用可能な仮説検定の中で最も科学的に厳密な方法であり、介入の効果を評価するためのゴールドスタンダードの試験と見なされている。

<!-- Note that in its idealized form, an RCT involves more than simply random assignment to treatment.  -->
理想的な形では、RCTは単に処置へのランダム割り当てを含む以上のものである。
<!-- Drawing on Akobeng (2005), we can enumerate the following as features of an ideal RCT: -->
Akobeng (2005)に基づいて、理想的なRCTの特徴として以下を挙げることができる。

<!-- 1. The treatments to be compared are specified in advance. -->
1. 比較する処置が事前に指定されている。
<!-- 2. The outcomes of interest are specified in advance. -->
2. 興味のある結果が事前に指定されている。
<!-- 3. Proposed analyses are specified in advance. -->
3. 提案された分析が事前に指定されている。
<!-- 4. The required number of participants is identified (using power calculations) in advance. -->
4. 必要な参加者数が事前に特定されている（パワー計算を使用）。
<!-- 5. Participants are recruited after required ethical approvals have been obtained. -->
5. 必要な倫理承認が得られた後に参加者が募集される。
<!-- 6. Participants are randomly assigned to treatment groups (we can consider the control as one of the treatments). -->
6. 参加者は処置群にランダムに割り当てられる（コントロールを処置の1つと考えることができる）。
<!-- 7. Participants do not know which treatment group they have been assigned to (concealment). -->
参加者はどの処置群に割り当てられたかを知らない（隠蔽）。
<!-- 8. Those administering treatment (e.g., doctors, nurses, researchers) do not know which treatment group participants have been assigned to (blinding). -->
処置を行う者（例：医師、看護師、研究者）は、参加者がどの処置群に割り当てられたかを知らない（ブラインディング）。

<!-- So random assignment treatment is only one of several components of an RCT.  -->
したがって、ランダム割当処置は、RCTのいくつかの構成要素の1つに過ぎない。
<!-- Even if we can argue that a candidate natural experiment offers as-if random assignment to treatment, a natural experiment will lack other features of an RCT. -->
候補となる自然実験が処置へのあたかもランダムな割り当てを提供すると主張できたとしても、自然実験にはRCTの他の特徴が欠けている。

<!-- First, the treatment is specified not by the researcher, but instead by firms, regulators, or “nature”, which we interpret broadly to include not only nature, but also complex economic forces perhaps not well understood by the researcher.  -->
第1に、処置は研究者によって指定されるのではなく、企業、規制当局、または「自然」によって指定される。ここで「自然」とは、自然だけでなく、研究者によって十分に理解されていないかもしれない複雑な経済的な力を含む広い解釈を意味する。
<!-- (We will often put the word “nature” in scare quotes to reinforce the broad interpretation the term is given in the context of natural experiments.)  -->
（自然実験の文脈で用いられる広い解釈を強調するために、「自然」という言葉を引用符で囲むことがよくある。）
<!-- This means that a researcher who “discovers” a natural experiment either needs to hope that the treatments that “nature” assigns are of interest to researchers or that other researchers can be persuaded that these treatments are of interest. -->
これは、自然実験を「発見」する研究者は、自然が割り当てる処置が研究者にとって興味深いものであることを期待するか、他の研究者にこれらの処置が興味深いものであると説得する必要があることを意味する。

<!-- Second, as a consequence of this, it is not meaningful in general to specify outcomes and analysis procedures in advance of the “experiment” being run.  -->
第2に、これにより、一般的には、「実験」が実施される前に結果と分析手順を事前に指定することは意味がない。
<!-- In many cases, the natural experiment is only identified after the experiment has been conducted.  -->
多くの場合、自然実験は実験が実施された後に特定される。
<!-- As a result, it is difficult to prevent p-hacking, which refers to processes in which researchers, whether consciously or not, consider a variety of outcomes and analytical procedures until “statistically significant” results are obtained.  -->
その結果、p-hackingを防ぐことが難しくなる。p-hackingとは、研究者が意識的であろうと無意識であろうと、さまざまな結果と分析手順を検討し、最終的に「統計的に有意な」結果を得るまでのプロセスを指す。
<!-- We discuss this limitation of natural experiments in more detail in Chapter 19. -->
自然実験のこの制限については、第19章で詳しく説明する。

<!-- Third, in general, natural experiments will not provide concealment of treatment assignment.1 -->
第3に、一般的に、自然実験は処置割り当ての隠蔽を提供しない。[^1]

<!-- However, we should note that concealment is not always meaningful in business research settings.  -->
ただし、隠蔽がビジネス研究の設定で常に意味があるわけではないことに注意する。
<!-- RCTs are often used to evaluate the drugs or other medical interventions that are expected to operate without conscious action by the participants.  -->
RCTは、参加者が意識的な行動なしに作用すると予想される薬剤やその他の医療介入を評価するためによく使用される。
<!-- In fact, it is because researchers are often most interested in the direct effect of the treatment unconfounded by other actions that the control group involves a **placebo** treatment as a control.  -->
実際、研究者が他の行動によって交絡されていない処置の直接的な効果に最も興味を持つことが多いため、コントロール群には**プラセボ**処置が含まれる。
<!-- But if the treatment of interest is an accounting standard, an incentive-compensation contract component, or financing constraints, then it’s not meaningful to speak of a direct, unconscious effect: if managers are unaware of features of their compensation contracts, then they are not going to take actions in response to them.  -->
しかし、興味のある処置が会計基準、インセンティブ報酬契約の構成要素、または資金調達制約である場合、直接的で無意識の効果について話すことは意味がない：マネージャーが自分の報酬契約の特徴に気づいていない場合、それに対応して行動を起こすことはない。
<!-- In general, it is likely that researchers are interested in the total effects of a treatment. -->
一般的に、研究者は総処置効果に興味を持っている可能性が高い。

<!-- Concealment of the fact of random assignment might be particularly important in settings involving **signalling**, as the response of the receiver of a signal is predicated on the signal being an endogenous response to the sender’s circumstances.  -->
ランダム割り当ての事実の隠蔽は、**シグナリング**を含む設定で特に重要かもしれない。なぜなら、シグナルの受信者の反応は、シグナルが送信者の状況に対する内生的な反応であることを前提としているからである。
<!-- If a signal is known by the receiver to have been randomly assigned, then there is no signalling value.  -->
シグナルが受信者にランダムに割り当てられたことが知られている場合、シグナリング価値はない。
<!-- As discussed by Armstrong et al. (2022), signalling has been used to explain patterns in voluntary disclosure, accounting choice, dividend policy, insider stock purchases, corporate social responsibility, and the decision to get an audit.2 -->
Armstrong et al. (2022)で議論されているように、シグナリングは、任意開示、会計選択、配当政策、インサイダー株式購入、企業の社会的責任、監査を受ける決定などのパターンを説明するために使用されてきた。[^2]

<!-- ### 17.1.2 Identifying the treatment of interest -->
### 興味のある処置の特定

<!-- Even when using an RCT, it can be difficult to ensure that the treatment applied is the one we are most interested in.  -->
ランダム化比較試行を使用していても、適用される処置が最も興味を持っているものであることを確実にすることは難しいことがある。
<!-- For example, suppose we’re interested in studying the effectiveness of KN95 masks in reducing the spread of Covid-19.  -->
たとえば、新型コロナウイルスの感染拡大を抑制するためのKN95マスクの効果を研究したいとしよう。
<!-- While a simple perspective might be that all we need to do for an experiment is to divide participants into treatment and control groups, in reality complexities exist. -->
実験のために参加者を処置群と対照群に分けるだけで済むという単純な視点があるかもしれないが、実際には複雑さが存在する。

<!-- One approach for the treatment group would be to issue all participants in this group with a supply of masks to be used during the study period and have participants go about their daily lives in other respects.  -->
処置群のアプローチの1つは、このグループのすべての参加者に研究期間中に使用するためのマスクを支給し、他の点では参加者が日常生活を送るようにすることである。
<!-- This implies that the treatment is “receive KN95 masks” rather than “wear KN95 masks”, even though the latter might be the treatment we are more interested in evaluating. -->
これは、「KN95マスクを着用する」がより興味を持って評価したい処置であるかもしれないにもかかわらず、「KN95マスクを着用する」ではなく「KN95マスクを受け取る」ということを意味している。

<!-- If we are interested in “wear KN95 masks” as the treatment, we might implement mechanisms for measuring whether masks are actually worn in practice.  -->
「KN95マスクを着用する」を処置として興味がある場合、実際にマスクが着用されているかどうかを測定するメカニズムを実装するかもしれない。
<!-- While this might be accomplished by sending out monitors to note whether masks are being worn properly, this would entail significant additional costs and it is unlikely that such data recording would be complete or even feasible (e.g., observing a participant at home or at work).  -->
これは、マスクが適切に着用されているかどうかを記録するためにモニターを送り出すことで達成できるかもしれないが、これにはかなりの追加費用がかかり、そのようなデータ記録が完全であるか、または実現可能であるかどうかは疑わしい（例：参加者を自宅や職場で観察する）。
<!-- Another approach would be to ask participants to maintain a log of their mask-wearing behaviour and rely on participants to be honest and diligent in doing so. -->
別のアプローチは、参加者にマスク着用の行動を記録するように依頼し、参加者が正直で熱心に行うことを期待することである。

<!-- As the recording of behaviour may itself influence behaviour (e.g., making a log may provide a reminder to wear a mask), this effectively alters the treatment to “receive KN95 masks and keep a log of mask-wearing”, which may not be of interest unless widespread logging of behaviour is considered part of the policy repertoire. -->
行動の記録自体が行動に影響を与える可能性があるため（例：記録を作成することでマスク着用を思い出させることができる）、これは事実上処置を「KN95マスクを受け取り、マスク着用の記録を保持する」と変更し、広範な行動の記録が政策のレパートリーの一部と見なされない限り、興味を持たれないかもしれない。

<!-- If we can only randomly assign participants to “receive KN95 masks” or not, and we are interested in “wear KN95 masks” as the treatment, an issue we need to consider is the reality that the conscientiousness with which participants wear masks is not random.  -->
参加者を「KN95マスクを受け取る」かどうかにランダムに割り当てることしかできず、「KN95マスクを着用する」を処置として興味がある場合、考慮する必要がある問題は、参加者がマスクを着用する熱心さがランダムではないという現実である。
<!-- Fortunately, with the right data, we can conduct an intention-to-treat analysis to evaluate the effect of “wear KN95 masks” even if we only have the ability to assign participants to “receive KN95 masks” as the treatment.  -->
幸いなことに、適切なデータがあれば、「KN95マスクを着用する」効果を評価するために、参加者を「KN95マスクを受け取る」処置に割り当てる能力しかない場合でも、意図治療分析を実施することができる。
<!-- This analysis uses instrumental variable techniques, which are the focus of Chapter 20, and further discussion of this approach is found in Chapters 4 and 5 of Dunning (2012). -->
この分析は、第20章の焦点である因果推定技術を使用しており、このアプローチについてのさらなる議論は、Dunning (2012)の第4章と第5章に見られる。

<!-- While it may be tempting to think of the control as simply the “no treatment” group, there are actually significant choices to be made in specifying the treatment depending on the specific treatment effect we wish to estimate.  -->
コントロールを単に「無処置」グループと考えることが誘惑されるかもしれないが、実際には、推定したい特定の処置効果に応じて処置を指定する際に重要な選択肢がある。
<!-- For example, wearing a mask may have an effect on Covid-19 transmission not because the mask physically prevents the transmission of the virus, but because wearing a mask may affect behaviour.  -->
たとえば、マスクを着用することがウイルスの伝播を物理的に防ぐからではなく、マスクを着用することが行動に影響を与える可能性があるため、マスクを着用することが新型コロナウイルスの伝播に影響を与えるかもしれない。
<!-- Wearing a mask might cause the wearer to be more cautious in interacting with others or, by making conversations more awkward, masks might reduce social interaction, or masks might cause others to give the wearer a wide berth (though this effect might have been more plausible in the pre-pandemic era).  -->
マスクを着用することで、着用者が他者とのやり取りにより慎重になる可能性があるかもしれないし、会話がより不自然になることで、マスクは社会的相互作用を減らすかもしれないし、マスクを着用することで他者が着用者に避ける可能性がある（ただし、この効果はパンデミック前の時代の方がより妥当であったかもしれない）。
<!-- Alternatively, masks might give wearers (and others) a sense of comfort and lead to increased social interaction.  -->
また、マスクは着用者（および他者）に安心感を与え、社会的相互作用を増加させる可能性がある。
<!-- And, as discussed above, if “receive KN95 masks and keep a log of mask-wearing” is the treatment, the control might be “receive no KN95 masks and keep a log of mask-wearing” on the assumption that some people will wear their own masks if none are provided.3 -->
また、上記で議論したように、「KN95マスクを受け取り、マスク着用の記録を保持する」が処置である場合、コントロールは「KN95マスクを受け取らず、マスク着用の記録を保持する」であると仮定すると、提供されない場合、一部の人々が自分自身のマスクを着用する可能性がある。[^3]

<!-- If we are interested in estimating the direct effect of KN95 masks on Covid-19 transmission, we might want to use a double-blind protocol (i.e., one with concealment and blinding) and specify the control treatment as “wear less effective masks” (in which case, the easy-to-estimate effect would be that of KN95 masks over less effective masks) or “wear completely ineffective marks” (in which case, the easy-to-estimate effect would be that of KN95 masks over ineffective masks, which may proxy for “no masks” in some ways).4 -->
新型コロナウイルスの伝播に対するKN95マスクの直接的な効果を推定することに興味がある場合、二重盲検プロトコル（つまり、隠蔽とブラインディングを備えたプロトコル）を使用し、コントロール処置を「効果の低いマスクを着用する」と指定することが望ましいかもしれない（この場合、推定しやすい効果は、効果の低いマスクよりもKN95マスクの効果である）または「完全に無効なマスクを着用する」と指定することが望ましいかもしれない（この場合、推定しやすい効果は、無効なマスクよりもKN95マスクの効果であり、これはある意味で「マスクなし」を代理するかもしれない）。[^4]

<!-- ### 17.1.3 Identifying the outcome of interest -->
### 興味のある結果の特定

<!-- Continuing our discussion of the hypothetical RCT with KN95 masks, the outcome of interest might seem obvious.  -->
KN95マスクを用いた架空のRCTに関する議論を続けると、興味のある結果は明らかに思えるかもしれない。
<!-- Perhaps we just need to track participants and measure the incidence of Covid-19 cases that are recorded.  -->
おそらく、参加者を追跡し、記録された新型コロナウイルスの感染症の発生率を測定するだけで十分である。
<!-- We are implicitly counting on certain things here, such as a reasonable baseline risk of getting Covid-19 with or without KN95 masks.  -->
我々はここでいくつかのことを暗黙的に前提としているが、それは、KN95マスクを着用しているかどうかに関係なく、新型コロナウイルスに感染するリスクが適度にあるということである。
<!-- Conducting a study with participants in an environment where Covid-19 has been eliminated during the study period is not likely to be helpful, as no one will get Covid-19 in either treatment condition.  -->
研究期間中に新型コロナウイルスが撲滅された環境で参加者を対象とした研究を行うことは有益ではない可能性が高い。なぜなら、どちらの処置条件でも誰も新型コロナウイルスに感染しないからである。
<!-- It is also important that the time over which symptoms appear is within the time frame of the study.  -->
また、症状が現れる期間が研究の期間内であることも重要である。
<!-- While Covid-19 infections may show up as infections within days, things are much more difficult with diseases whose symptoms show up years after exposure to risk factors. -->
新型コロナウイルス感染症は数日以内に感染として現れるかもしれないが、症状がリスク要因にさらされてから数年後に現れる疾患では、事態ははるかに困難である。

<!-- But if masks affect not only the incidence of cases, but also their seriousness of cases that occur, then we likely need to track additional indicators, such as hospitalizations with Covid-19, serious health issues, and deaths. -->
しかし、マスクが症例の発生率だけでなく、発生した症例の重症度にも影響を与える場合、新型コロナウイルスによる入院、重篤な健康問題、死亡などの追加の指標を追跡する必要があるかもしれない。

<!-- More complicated is the issue that the outcome of interest might be the effect of mask-wearing on the incidence or severity of disease in others.  -->
さらに複雑なのは、興味のある結果が他者の疾病の発生率や重症度に対するマスク着用の効果である可能性があることである。
<!-- Adopting this as the outcome of interest implies significant changes to the treatment-assignment approach and measures tracked, as it would likely be impractical to assign treatment to participants and track the health outcomes of the people with whom they interact.  -->
これを興味のある結果として採用すると、処置割り当てアプローチと追跡される指標に重大な変更が必要になる可能性がある。なぜなら、参加者に処置を割り当て、彼らが相互作用する人々の健康結果を追跡することは実用的ではないからである。
<!-- Instead, it is likely that outcomes would be narrowed in scope (e.g., the transmission of disease in the office or at school rather than in general) and treatment assignment done at a level higher than individuals (e.g., schools or offices). -->
代わりに、結果は範囲が狭められる可能性が高い（例：一般的な疾病の伝播ではなく、オフィスや学校での疾病の伝播）し、処置割り当ては個人よりも高いレベル（例：学校やオフィス）で行われる可能性が高い。

<!-- ### 17.1.4 Laboratory experiments -->
### 実験室実験


<!-- The hypothetical experiments described above are analogous to field experiments, which involve real decision-makers making real decisions in the relevant context.  -->
上記で説明した架空の実験は、関連する文脈で実際の意思決定者が実際の意思決定を行うフィールド実験に類似している。
<!-- More common in accounting research is the laboratory experiment.  -->
会計研究では、より一般的なのは実験室実験である。
<!-- A typical laboratory experiment involves participants of convenience (e.g., undergraduate students or online survey participants) making “decisions” in a highly stylized setting. -->
典型的な実験室実験は、便宜的な参加者（例：大学生やオンライン調査参加者）が非常にスタイライズされた環境で「意思決定」を行うことを含む。

<!-- The analogy with RCTs can be seen by considering how challenging it would be to evaluate KN95 masks or Covid vaccines in a pure laboratory setting.  -->
RCTとの類似性は、純粋な実験室環境でKN95マスクや新型コロナウイルスワクチンを評価することがどれほど困難であるかを考えることで見ることができる。
<!-- While one could certainly issue masks or administer vaccines in a laboratory setting, a highly controlled laboratory environment is not a setting in which participants would be expected to encounter the SARS-CoV-2 virus, making it useless as a setting for evaluating the effectiveness of prophylactic measures such as masks or vaccines.  -->
確かに、実験室環境でマスクを支給したりワクチンを投与することはできるが、高度に制御された実験室環境は、参加者が新型コロナウイルスに遭遇することが期待されない環境であり、マスクやワクチンなどの予防措置の効果を評価するための環境としては役に立たない。
<!-- Furthermore, the period over which one needs to be potentially exposed to the SARS-CoV-2 virus is measured in weeks and months, likely further ruling out a laboratory setting.5 -->
さらに、新型コロナウイルスに潜在的にさらされる必要がある期間は数週間から数か月であり、おそらく実験室環境をさらに排除する。[^5]
<!-- As a result, most RCTs would involve field experiment elements with participants entering their normal environment after treatment assignment and administration. -->
結果として、ほとんどのRCTは、処置割り当てと投与後に参加者が通常の環境に入るフィールド実験要素を含む。

<!-- While laboratory experiments might be useful for understanding generic features of human decision-making, it is a huge leap to go from the reactions of undergraduates to hypothetical accounting policy variables and hypothetical investment decisions to conclusions about real-world business decisions.  -->
実験室実験は、人間の意思決定の一般的な特徴を理解するために有用であるかもしれないが、大学生の反応から架空の会計政策変数や架空の投資決定に関する結論を導くことは、実世界のビジネスの意思決定についての結論には大きな飛躍である。
<!-- This is arguably true for almost all research questions examined by accounting researchers.  -->
これは、会計研究者が検討するほとんどの研究問題に当てはまると言える。
<!-- Consistent with this, the impact of research using laboratory experiments on empirical accounting research—the overwhelming majority of research in the top accounting journals (see Gow et al., 2016)—seems fairly limited. -->
これに一貫して、実験室実験を使用した研究の会計実証研究への影響は、トップの会計ジャーナルのほとんどの研究（Gow et al., 2016を参照）において非常に限られているように思われる。

<!-- ## 17.2 Natural experiments -->
## 自然実験


<!-- Natural experiments occur when observations are assigned by nature (or some other force outside the control of the researcher) to treatment and control groups in a way that is random or “as if” random (Dunning, 2012).  -->
自然実験は、観察が自然（または研究者のコントロール外の他の力）によって処置群と対照群にランダムまたは「まるで」ランダムに割り当てられるときに発生する（Dunning, 2012）。
<!-- If such assignment is (as-if) random, then natural experiments can function much like field experiments for the purposes of causal inference. -->
このような割り当てが（まるで）ランダムである場合、自然実験は因果推論の目的においてフィールド実験と同様に機能することができる。

<!-- Dunning (2012, p.3, emphasis added) argues that the appeal of natural experiments “may provoke conceptual stretching, in which an attractive label is applied to research designs that only implausibly meet the definitional features of the method.”  -->
Dunning (2012, p.3)は、「自然実験の魅力は、定義的な特徴を信じがたいほど満たす研究デザインに魅力的なラベルが適用される可能性があるため、概念的な拡張を引き起こすかもしれない」と主張している。
<!-- As we discuss below, such conceptual stretching seems common in accounting research. -->
以下で議論するように、このような概念的な拡張は、会計研究では一般的であるように思われる。

<!-- One dimension along which stretching concerns claims of as-if random assignment.  -->
懸念される概念的な拡張の1つの側面は、まるでランダムな割り当ての主張である。
<!-- In some cases, ignorance of the assignment mechanism appears to substitute for a careful evaluation of how random it is, which requires a deep understanding of that mechanism.  -->
いくつかの場合、割り当てメカニズムの無知が、そのメカニズムの深い理解を必要とするランダム性の詳細な評価の代わりになるように見える。
<!-- While the process by which a coin lands on heads or tails is mysterious, the randomness of the coin toss is predicated on a deep understanding that the coin is fair (i.e., equally likely to come up heads or tails). -->
コインが表か裏になるプロセスは神秘的であるが、コイントスのランダム性は、コインが公平である（つまり、表か裏が同じくらいの確率で出る）という深い理解に基づいている。

<!-- The discussion of RCTs above was not intended to be a primer on conducting randomized controlled trials or field experiments.  -->
上記のRCTに関する議論は、ランダム化比較実験やフィールド実験の実施方法に関する入門的な説明を目的としたものではない。
<!-- Instead, the goal was to flag how merely randomizing treatment assignment is only one element—albeit a critical one—of a well-designed field experiment.  -->
その代わりに、処置割り当てを単にランダム化することは、よく設計されたフィールド実験の要素の1つであるに過ぎないことを示すことが目的であった。
<!-- In evaluating a natural experiment, a researcher needs to consider the issues raised in field experiments, even if these elements cannot be adjusted through choices of the researcher. -->
自然実験を評価する際には、研究者が選択肢を通じて調整することができない場合でも、フィールド実験で提起された問題を考慮する必要がある。

<!-- For example, what “nature” (seemingly) randomizes often is not exactly the variable researchers might be interested in studying.  -->
たとえば、「自然」が（見かけ上）ランダム化する変数は、研究者が研究したいと考える変数とは必ずしも一致しないことがよくある。
<!-- As we saw above, even in field experiments, careful consideration of the precise treatments to consider is required and it seems unlikely that “nature” is going to make choices that align with what a researcher would make.  -->
上記で見たように、フィールド実験でも、検討すべき正確な処置を慎重に考慮する必要があり、研究者が選択するものと一致する選択を「自然」が行う可能性は低いように思われる。
<!-- One response to this is for researchers to argue that what nature has randomized is the thing of interest.  -->
これに対する1つの対応策は、研究者が自然がランダム化したものが興味の対象であると主張することである。
<!-- Another response to suggest that the thing randomized is equivalent to something else that is of interest.  -->
興味のあるものと同等であると主張するための別の対応策もある。
<!-- Finally, in some cases, the variable randomized by “nature” might satisfy the requirements of an instrumental variable, something we examine in Chapter 20. -->
最後に、一部の場合では、「自然」によってランダム化された変数が、因果推定の要件を満たすことがある。これについては、第20章で詳しく調べる。

<!-- ### 17.2.1 Natural experiments in accounting research -->
### 会計研究における自然実験


<!-- In a survey of accounting research in 2014, Gow et al. (2016) identified five papers that exploited either a “natural experiment” or an “exogenous shock” to identify causal effects. -->
2014年の会計研究のサーベイにおいて、Gow et al. (2016)は、「自然実験」または「外生的ショック」を利用して因果効果を特定するために利用された5つの論文を特定した。
<!-- But Gow et al. (2016) suggest that closer examination of these papers “reveals how none offers a plausible natural experiment.” -->
しかし、Gow et al. (2016)は、これらの論文をより詳しく調べると、「どれも信憑性のある自然実験を提供していないことが明らかになる」と述べている。


<!-- The main difficulty is that most “exogenous shocks” (e.g., SEC regulatory changes or court rulings) do not randomly assign units to treatment and control groups and thus do not qualify as natural experiments.  -->
主な困難な点は、ほとんどの「外生的ショック」（例：SECの規制変更や裁判所の判決）は、処置群と対照群に単位をランダムに割り当てるわけではないため、自然実験として適格ではないことである。
<!-- For example, an early version of the Dodd-Frank Act contained a provision that would force US companies to remove a staggered board structure.6  -->
たとえば、Dodd-Frank法の初期バージョンには、米国企業に対してスタッガード・ボード構造を撤廃するように強制する規定が含まれていた。[^6]
<!-- It might be tempting to use this event to assess the valuation consequences of having a staggered board by looking at excess returns for firms with and without a staggered board around the announcement of this Dodd-Frank provision.  -->
この出来事を利用して、スタッガード・ボードを有する企業と有しない企業の超過収益を、このDodd-Frank規定の発表前後に見ることで、スタッガード・ボードの評価結果を評価することは誘惑されるかもしれない。
<!-- Although potentially interesting, this purported “natural experiment” does not randomly assign firms to treatment and control groups. -->
これは潜在的に興味深いかもしれないが、この自称「自然実験」は企業を処置群と対照群にランダムに割り当てるわけではない。

<!-- In addition, it is important to carefully consider the choice of explanatory variables in studies that rely on natural experiments.  -->
さらに、自然実験に依存する研究で説明変数の選択を慎重に考慮することが重要である。
<!-- In particular, researchers sometimes inadvertently use covariates that are affected by the treatment in their analysis.  -->
特に、研究者は、時々、分析において処置に影響を受ける共変量を誤って使用している。
<!-- As noted by Imbens and Rubin (2015, p.116), including such post-treatment variables as covariates can undermine the validity of causal inferences.7 -->
Imbens and Rubin (2015, p.116)によると、処置後の変数を共変量として含めることは、因果推論の妥当性を損なう可能性がある。[^7]

<!-- One plausible natural experiment flagged by Gow et al. (2016) is Li and Zhang (2015).  -->
Gow et al. (2016)によって指摘された可能性のある自然実験の1つは、Li and Zhang (2015)である。
<!-- Li and Zhang (2015, p.80) study a regulatory experiment (Reg SHO) in which the SEC “mandated temporary suspension of short-sale price tests for a set of randomly selected pilot stocks.”  -->
Li and Zhang (2015, p.80)は、SECが「一連の無作為に選択されたパイロット株式に対してショートセール価格テストの一時的な停止を命じた」という規制実験（Reg SHO）を研究している。
<!-- Li and Zhang (2015, p.79) conjecture “that managers respond to a positive exogenous shock to short selling pressure … by reducing the precision of bad news forecasts.”  -->
Li and Zhang (2015, p.79)は、「マネージャーがショートセール圧力に対するポジティブな外生的ショックに反応して、悪いニュースの予測の精度を低下させる」と推測している。
<!-- But if the treatment affects the properties of these forecasts, and Li and Zhang (2015) sought to condition on such properties, they would risk undermining the “natural experiment” aspect of their setting.  -->
しかし、処置がこれらの予測の特性に影響を与え、Li and Zhang (2015)がその特性に依存しようとすると、「自然実験」の側面を損なうリスクがある。
<!-- We examine Reg SHO in more detail in Chapter 19. -->
Reg SHOについては、第19章で詳しく調べる。

<!-- Michels (2017) is another plausible natural experiment identified by Gow et al. (2016) and we investigate it further below. -->
Michels (2017)は、Gow et al. (2016)によって特定された別の可能性のある自然実験であり、以下でさらに調査する。



<!-- ## 17.3 Recognition versus disclosure -->
## 認識と開示

<!-- One of the longest-standing questions in accounting research is whether it matters whether certain items are recognized in financial statements or merely disclosed in, say, notes to those financial statements.  -->
会計研究における最も長期にわたる問題の1つは、特定の項目が財務諸表に認識されるか、たとえば、それらの財務諸表の注記に開示されるかどうかが重要かどうかということである。
<!-- As the following vignettes illustrate, debates about recognition versus disclosure have been some of the most heated in financial reporting. -->
以下の短い例が示すように、認識と開示に関する議論は、財務報告において最も激しいものの1つである。

<!-- ### 17.3.1 Stock-based compensation -->
### 株式報酬

<!-- Accounting for stock-based compensation is one of the most controversial topics ever addressed by accounting standard-setters.  -->
株式報酬の会計処理は、会計基準制定機関が取り組んだ中で最も論争の的となったトピックの1つである。
<!-- In 1973, the US Financial Accounting Standards Board (FASB) issued APB 25, which required firms to measure the expense as the difference between the stock price and the option exercise price on the grant date (or “intrinsic value”), which equals zero for most employee options.  -->
1973年、米国財務会計基準委員会（FASB）は、株価とオプション行使価格の差（または「内在価値」）をオプションの付与日に測定することを企業に要求するAPB 25を発行した。この内在価値は、ほとんどの従業員オプションに対してゼロに等しい。
<!-- In 1993, the FASB issued an exposure draft proposing that firms measure the expense based on the options’ grant date fair value.  -->
1993年、FASBは、企業がオプションの付与日の公正価値に基づいて費用を測定することを提案する公開草案を発行した。
<!-- While APB 25 predated Black and Scholes (1973), approaches to measuring the fair value of options were widely accepted and understood by 1993.  -->
APB 25はBlack and Scholes（1973）より前に発行されたが、1993年までには、オプションの公正価値を測定する方法は広く受け入れられ、理解されていた。
<!-- This exposure draft met with fierce resistance by firms, and the US Congress held hearings on whether the FASB should be permitted to finalize the standard as proposed. -->
この公開草案は、企業から激しい抵抗を受け、米国議会は、FASBが提案された通りに基準を最終化することを許可すべきかどうかについての公聴会を開催した。

<!-- In 1995, the FASB issued SFAS 123, which preferred measurement of the expense using the grant-date fair value, but allowed firms to recognize the expense using the APB 25 measurement approach and only disclose what net income would have been had the expense been measured using the grant-date fair value approach.  -->
1995年、FASBは、費用を付与日の公正価値を使用して測定することを好むが、企業が費用を付与日の公正価値アプローチを使用して測定した場合の純利益がいくらであったかを開示するだけで、APB 25の測定アプローチを使用して費用を認識することを許可するSFAS 123を発行した。
<!-- In its basis for conclusions, the FASB admitted that it did not require expense recognition because the severity of the controversy was such that doing so might have threatened accounting standard-setting in the private sector. -->
FASBは、その根拠について、プライベート・セクターの会計基準設定を脅かす可能性があるため、費用認識を要求しなかったと認めた。

<!-- Almost all firms applied the measurement approach of APB 25 until the summer of 2002 when a small number of firms adopted the grant date value approach (Aboody et al., 2004; Brown and Lee, 2011).  -->
ほとんどの企業は、2002年の夏までAPB 25の測定アプローチを適用していたが、2002年の夏に一部の企業が付与日価値アプローチを採用した（Aboody et al., 2004; Brown and Lee, 2011）。
<!-- In light of the financial reporting failures of 2001, the FASB revisited accounting for stock-based compensation and, in 2004, the FASB issued SFAS 123R, which took effect for fiscal years beginning on or after June 15, 2005.  -->
2001年の財務報告の失敗を踏まえ、FASBは株式報酬の会計処理を再検討し、2004年にSFAS 123Rを発行した。この基準は、2005年6月15日以降に開始される会計年度に効力を発揮した。
<!-- The primary effect of SFAS 123R was to require recognition of stock-based compensation expense using the grant-date fair value. -->
SFAS 123Rの主な効果は、付与日の公正価値を使用して株式報酬費用を認識することを要求することであった。

But, even after SFAS 123R was adopted, controversy continued.
Several prominent persons, including former US cabinet secretaries and three Nobel laureates, reiterated arguments that recognizing the expense is improper because the value of employee stock options does not represent an expense of the firm (Hagopian, 2006) and filed a petition with the SEC in 2008 alleging that the SEC failed in its duties by permitting the FASB to issue SFAS 123R.

<!-- ### 17.3.2 Accounting for leases -->
### リースの会計処理

<!-- A lease is an agreement between a lessor who owns an asset and a lessee that grants the lessee the right to use the asset for a period of time in exchange for (typically periodic) payments.  -->
Leasing is a huge business around the globe, and leases are a common way for firms to acquire the right to use assets such as real estate, aircraft, and machinery.

Leasing an asset is often an alternative to buying that asset.
If a firm only needs an asset for a short period of time, then leasing the asset may reduce transaction costs and eliminate risks associated with the value of the asset at the end of the lease.
Lessors are often firms with specialist expertise in managing the acquisition, leasing, and disposal of assets and understanding how their value changes over their useful lives.

In some circumstances, the economic risk and benefits of asset ownership are borne by the lessee.
For example, if a lease includes a bargain purchase option that a rational lessee will almost certainly exercise or if title to the asset simply transfers to the lessee at the end of the lease, then the lessee owns the asset in any relevant economic sense.

However, like any contract, a lease has two sides.
Generally lessee acquires economic ownership of an asset in exchange for a stream of payments over time.
In many leases, the payments are periodic and fixed.
Anyone who has mortgaged a house or financed a vehicle purchase will likely recognize an obligation for fixed and periodic payments as a loan.

Thus, in some cases, a lease is economically equivalent to the combination of two transactions: first, borrowing money on a loan that requires fixed, periodic repayments and, second, use of the loan proceeds to acquire the leased asset.

SFAS 13 (later relabelled as ASC 840), which was issued by the US Financial Accounting Standards Board in 1976, required leases with features that made them more akin to purchases of assets financed by loans to be accounted for in a manner essentially equivalent to loan-backed asset purchases.
SFAS 13 specified criteria, such as the transfer of asset ownership at the end of the lease or the presence of a bargain purchase option, that would trigger this capital lease accounting treatment.

Under capital lease accounting, a leased asset and a lease liability would be recognized on the balance sheet.
The leased asset would be depreciated (or “amortized” in the language of SFAS 13) “in a manner consistent with the lessee’s normal depreciation policy” over the lease term.
At the same time, “each minimum lease payment shall be allocated between a reduction of the obligation and interest expense so as to produce a constant periodic rate of interest on the remaining balance of the obligation.”

SFAS 13 provided that leases not meeting the criteria for capital lease accounting should be accounted for as operating leases.
For such leases, no asset or liability would be recognized and, for most leases, the standard provided that “rental on an operating lease shall be charged to expense over the lease term as it becomes payable.”

In 2004, Jonathan Weil wrote in the Wall Street Journal that “companies are still allowed to keep off their balance sheets billions of dollars of lease obligations that are just as real as financial commitments originating from bank loans and other borrowings.” While SFAS 13 classified leases that were obviously economically equivalent to debt-financed asset purchases, its criteria allowed firms to structure leases so that they were economically very close to such purchases, but which were classified as operating leases for financial reporting purposes.
Weil flagged US retail pharmacy chain Walgreen, which “shows no debt on its balance sheet, but it is responsible for $19.3 billion of operating-lease payments mainly on stores over the next 25 years” and stated that the off-balance-sheet operating-lease commitments, as revealed in the footnotes to their financial statements for companies in the Standard & Poor’s 500-stock index totalled US$482 billion.

In 2006, the FASB began work on a new lease accounting standard intended to close “loopholes” like those described by Weil.
Given the extensive information about operating leases provided under SFAS 13, we can view SFAS 13 as providing disclosure of operating leases, whereas many called for their recognition on the balance sheet.

In 2016, FASB published a new lease accounting standard, ASC 842, and the IASB issued a similar standard, IFRS 16.
These accounting standards require all leases to be brought onto the balance sheet (except short-term leases).

<!-- ### 17.3.3 Academic research -->
### 学術研究

The two examples above serve two purposes.
First, they highlight the significance of recognition-versus-disclosure questions in financial reporting.
Second, they provide concrete settings for thinking about some subtle issues faced by researchers in studying the topic of recognition versus disclosure.
As we shall see, some of these subtleties would exist even if we could run any field experiment we could conceive.

What do “recognition” and “disclosure” mean? Simplistically, the choice between recognition and disclosure is a choice between including a given amount in the financial statements or merely disclosing the amount, typically in the footnotes to the financial statements.
However, as pointed out by Bernard and Schipper (1994), the choice is significantly more complicated than this simple binary “in or out” election.
FASB’s Statement of Financial Accounting Concepts No 5 (SFAC 5) defines recognition as “the process of formally incorporating an item in the financial statements of an entity as an asset, liability, revenue, expense, or the like.
A recognized item is depicted in both words and numbers, with the amount included in the statement totals.”

Paragraph 5.1 of the IASB Conceptual Framework contains a similar definition, but clarifies certain elements of the FASB definition.
First, recognition involves the statements of financial position and financial performance; putting an item in the statement of cash flows alone would not seem to constitute recognition.
Second, “or the like” is clarified to mean “equity”, as this rounds out the list of elements of financial statements.
Third, “numbers” mean monetary amounts, as this is how elements are put in financial statements.
Implicit in both definitions is that the monetary amounts can be added up in some meaningful fashion, as financial statement items are included as components of sums.

Bernard and Schipper (1994) note that “recognition does not appear to have a formal definition in the FASB’s official pronouncements” [p.
4], and the same appears to be true of the IASB Conceptual Framework.
Instead, Bernard and Schipper (1994) suggest that “one could view recognition as a form of disclosure with special characteristics” [p.
5].

Can recognition and disclosure be viewed as alternatives? Bernard and Schipper (1994) suggest that if we take the conceptual frameworks as binding constraints on standard-setters, then recognition versus disclosure cannot be viewed as a choice.
Either an item meets the recognition criteria and thus must be recognized, or it does not and thus must not be recognized.
But it is unclear whether the conceptual frameworks determine standards to this degree.
Nothing in SFAC 5 changed between SFAS 123 and SFAS 123R, even though the two standards came out on opposite sides with regard to recognition of stock-based compensation expense.8

The case of SFAS 123 above is arguably one of the sharpest instances of recognition versus disclosure.
Under SFAS 123, a firm that used the APB 25 approach to measuring the cost of employee stock options was required to provide a pro forma disclosure of the expense in the footnotes to its financial statements.9 In effect, a firm must provide the information that it would have provided had it recognized an expense using the fair-value approach.
While the pro forma financial statements only include the statement of financial performance, there is no aggregate impact of applying the SFAS 123 approach on the statement of financial position, as the debit to expense, which would flow through net income to retained earnings, is offset by an addition to additional paid-in capital.

The case of lease accounting is perhaps more typical of recognition-versus-disclosure settings.
First, firms cannot elect to apply operating lease accounting instead of capital lease accounting.
If a lease is a capital lease, then capital lease accounting must be applied.
If a lease is not a capital lease, then operating lease accounting must be applied.
(That said, under SFAS 13, firms would often structure their leases such that a minor tweak to the lease would cause it to switch from one accounting treatment to the other.)

Second, there was no equivalent requirement under SFAS 13 to the pro forma disclosures provided under SFAS 123.
Such pro forma disclosures would need to be extensive, as lease accounting under SFAS 13 affected the statement of financial position, the statement of financial performance, and the statement of cash flows.
Instead, firms were required to disclose rental expense related to operating leases, minimum rental payments in aggregate and for each of the five succeeding fiscal years and a general description of leasing arrangements, such as details about contingent rental payments, renewal or purchase options, and escalation clauses.

Why might recognition versus disclosure matter? Focusing for the moment on the implications of recognition versus disclosure for capital markets, there are two theories at opposites ends of a spectrum.

According to Watts (1992), “the mechanistic hypothesis posits that stock prices react mechanically to the reported earnings number, regardless of how the number is calculated.” (A natural generalization of the mechanistic hypothesis would be to apply it to reported balance sheet numbers and financial ratios based on reported numbers in financial statements.) At the other end of the spectrum is the efficient markets hypothesis (EMH), which in its semi-strong form posits that capital markets efficiently process all publicly available information and impound that information into security prices.

Under the mechanistic hypothesis, if numbers are disclosed in footnotes but not recognized in financial statements, the market will not respond to them.
In contrast, under the EMH, markets will react to information whether it is recognized or disclosed.

Implicit in the last sentence is the assumption that the information content is unaffected by the recognition-versus-disclosure decision.
But this may not be true for a number of reasons.

First, the information content may differ due to the aggregation and conversion of disclosed amounts into monetary amounts that occur as part of the recognition process.
In the case of operating leases, future lease payments are discounted and added up to form the liability recognized on the balance sheet.
Additionally, assets are depreciated and reported at net carrying value.
These calculations are difficult for an outsider to replicate precisely using disclosed information (e.g., due to imprecise information about the timing of rental payments and discount rates), and their results may convey useful information to market participants.

Second, even if the notional information content does differ between recognition and disclosure, the recognition-versus-disclosure decision may affect the information properties of the information due to differences in behaviour across the two conditions.
For example, managers may view recognized information as more consequential and thus may exert more effort to produce more accurate numbers (or more effort on earnings management).
Auditors may also view their obligations to provide assurance for recognized numbers to be greater than that for their merely disclosed equivalents.

Even if the EMH holds, if managers or others do not believe that it holds and instead assume that the mechanistic hypothesis better describes reality, they act accordingly.
In the lead-up to SFAS 123R, many firms accelerated the vesting of stock options to avoid reporting expenses.
The economic consequences of this action were fairly clear (essentially a wealth transfer from firms to employees), and Choudhary et al.
(2009) find that the market reacted accordingly when acceleration decisions were announced.
Yet Choudhary et al.
(2009) quote the perspective of one firm (Central Valley Community Bancorp) that is firmly grounded in the mechanistic view:

The Board believes it was in the best interest of the shareholders to accelerate these options, as it will have a positive impact on the earnings of the Company over the previously remaining vested period of approximately 3 years.

Designing experiments to study recognition versus disclosure.
Given the various ways in which recognition versus disclosure can matter, a regulator seeking to run field experiments to understand the merits of various policies is confronted with a variety of possible experiments to run.
Knowing that recognition matters relative to disclosure is not very useful if it is not coupled with some understanding of why it matters, which is tantamount to understanding the causal mechanism.
This is important because the appropriate experimental design will vary according to the causal mechanism that is sought to be tested.

The best way to see how experimental design should vary by the conjectured mechanism is to consider some specific cases.
If we conjecture that recognition matters because of difficulties that investors have in processing disclosed-but-not-recognized footnote information into pro forma financial statement information, we might divide firms into three groups: firms that recognize in financial statements; and firms that do not recognize but disclose pro forma information in the footnotes (à la SFAS 123); firms that disclose information in the footnotes that requires additional processing or detail to calculate pro forma financial information (similar to disclosure of operating leases under SFAS 13).

<!-- ## 17.4 Michels (2017)  -->
## Michels (2017)

In this chapter so far, we have covered experiments, including natural experiments, and the broader question of recognition versus disclosure.
Now we turn to Michels (2017), who studies one aspect of recognition versus disclosure using a plausible natural experiment.

Michels (2017) exploits the difference in disclosure requirements for significant events that occur before financial statements are issued.
Because the timing of these events (e.g., fires and natural disasters) relative to balance sheet dates is plausibly random, the assignment to the disclosure and recognition conditions is plausibly random.

The data set michels_2017 from the farr package provides information about the 423 observations in Michels (2017).
For 343 of these observations, the natural disaster occurred after the relevant filing for the previous financial period was made, and thus the financial effects are recognized in the current period.
For the remaining 80 cases, the natural disaster occurred before the relevant filing for the previous financial period was made, and thus the financial effects are disclosed in that filing (and recognized in a subsequent filing containing financials for the current period).

<!-- Figure 17.1 depicts the distribution of the number of days between the applicable natural disaster and the next filing date. -->
図17.1は、該当する自然災害と次の提出日の間の日数の分布を示している。

```{r}
#| eval: false

michels_2017 |>
  mutate(days_to_filing = as.integer(date_filed - eventdate)) |>
  ggplot(aes(x = days_to_filing, fill = recognize)) +
  geom_histogram(binwidth = 1)
```

<!-- Figure 17.2 depicts the distribution of the number of days between the applicable natural disaster and days to the end of the fiscal period in which it occurs. -->
図17.2は、該当する自然災害とその発生した財務期間の終了日との日数の分布を示している。


```{r}
#| eval: false

michels_2017 |>
  mutate(days_to_period_end = as.integer(next_period_end - eventdate)) |>
  ggplot(aes(x = days_to_period_end, fill = recognize)) +
  geom_histogram(binwidth = 1)
```

<!-- bviously major natural disasters can affect more than one firm and Table 17.1 provides data on the five most common disaster dates in the Michels (2017) sample. -->
明らかに、大規模な自然災害は1つ以上の企業に影響を与える可能性があり、表17.1はMichels (2017)のサンプルにおける最も一般的な災害日に関するデータを提供している。

```{r}
#| eval: false

michels_2017 |>
  count(eventdate) |>
  arrange(desc(n)) |>
  top_n(5)
```

<!-- ## 17.5 Discussion questions -->
## ディスカッション課題

<!-- 1. One assumption in Michels (2017) is that whether a natural disaster occurs before or after the balance sheet date of the next filing is random.  -->
1. Michels (2017)の仮定の1つは、次の提出の貸借対照表日の前後に自然災害が発生するかどうかがランダムであるということである。
<!-- Do the inherent properties of natural disasters ensure that they are random? Why?  -->
自然災害の固有の特性は、それらがランダムであることを保証するか？なぜか？
<!-- If not, how would you evaluate the randomness of natural disasters in the sample of Michels (2017)?  -->
そうでない場合、Michels (2017)のサンプルにおける自然災害のランダム性をどのように評価するか？
<!-- Do the analyses above help this evaluation? -->
上記の分析は、この評価に役立つのか？

<!-- 2. Describe what you imagine to be the process from the occurrence of a natural disaster to reporting on that event in the subsequent filing?  -->
2. 自然災害の発生からその出来事についての報告までのプロセスを想像して説明しなさい。
<!-- Do you think this process differs for recognized versus disclosed events? -->
認識されたイベントと開示されたイベントでは、このプロセスが異なると考えるか？

<!-- 3. From the analysis, above it appears that five natural disasters account for 228 observations.  -->
3. 上記の分析から、5つの自然災害が228の観測値を占めているように見える。
<!-- A simple Google search for each date and the word “disaster” reveals that these events are Hurricane Katrina (2005-08-29), Hurricane Ike (2008-09-13), Hurricane Ivan (2004-09-16), Hurricane Charley (2004-08-13), and Hurricane Wilma (2005-10-24).  -->
各日付と「災害」という単語のシンプルなGoogle検索により、これらのイベントがハリケーン・カトリーナ（2005年8月29日）、ハリケーン・アイク（2008年09月13日）、ハリケーン・アイバン（2004年09月16日）、ハリケーン・チャーリー（2004年08月13日）、ハリケーン・ウィルマ（2005年10月24日）であることがわかる。
<!-- Is it problematic that a small number of disasters accounts for a significant portion of the sample? -->
サンプルの大部分を占める少数の災害が問題であるか？

<!-- 4. Where does Michels (2017) get data on natural disasters from? Is there anything that is problematic about this data source? Would it be possible to use another approach to data collection? What challenges would that approach face? -->
4. Michels (2017)は自然災害に関するデータをどこから入手しているのか？このデータソースに問題があるか？データ収集に別のアプローチを使用することは可能か？そのアプローチはどのような課題に直面するか？

<!-- 5. A recurring question in accounting is if it matters whether information is disclosed or recognized.  -->
5. 会計において繰り返し問われるのは、情報が開示されるか認識されるかが重要かどうかということである。
<!-- One view is that, if markets are efficient, it should not matter where the information is disclosed, so recognition should not matter relative to disclosure.  -->
もし市場が効率的であれば、情報が開示される場所は問題にならないはずであり、したがって、認識は開示に対して重要ではないはずである。
<!-- What assumptions underlie this view?  -->
この見解の背後にある仮定は何か？
<!-- Are there any reasons to believe that they do or do not hold in the setting of Michels (2017)?  -->
Michels (2017)の設定では、それらが成立するかどうかを信じる理由はあるか？
<!-- What are the implications for the ability of Michels (2017) to deliver clean causal inferences?  -->
Michels (2017)がクリーンな因果推論を提供する能力にはどのような影響があるか？
<!-- How might materiality criteria differ for disclosed and recognized events?  -->
開示されたイベントと認識されたイベントに対する重要性基準はどのように異なるか？
<!-- Would differences in these criteria affect the empirical analysis of Michels (2017)? -->
これらの基準の違いは、Michels (2017)の実証分析に影響するか？

<!-- 6. What causal inferences does Michels (2017) draw? What (if any) issues do you see with regard to these? -->
6. Michels (2017)はどのような因果推論を導いているか？これらに関してどのような問題があるか（あれば）？

<!-- 7.  Choose a paper that you have seen recently that uses empirical analysis of non-experimental data. (If you cannot choose such a paper, Hopkins et al. (2022) provide one option.) Looking at the abstract of the paper, can you determine whether this paper seeks to draw causal inferences? -->
7. 最近見た、非実験データの実証分析を使用している論文を選択しなさい。（そのような論文を選択できない場合、Hopkins et al. (2022)が1つの選択肢を提供している）論文の要約を見ると、この論文が因果推論を導こうとしているかどうかを判断できますか？

<!-- 8. Choose what you think the authors regard to be the most important causal inference they draw (or would like to draw) in your chosen paper.  -->
8. 選択した論文で、著者が最も重要だと考えている（または描きたい）と思われる因果推論を選択しなさい。
<!-- Which table or tables provide the relevant empirical analyses?  -->
どの表が関連する実証分析を提供していますか？
<!-- Sketch a rough causal diagram for this causal inference using either discussion in the paper or your own background knowledge to identify important variables.  -->
この因果推論について、論文の議論または自分のバックグラウンド知識を使用して重要な変数を特定し、おおまかな因果図をスケッチしなさい。
<!-- How credible do you find the reported causal inferences to be in light of your causal diagram? -->
あなたの因果図を考慮して、報告された因果推論をどの程度信頼性があると考えるか？

